LOSA Fuel Poverty maps

### 2021-09-02 LSOA Fuel poverty.Rmd
fixed for now

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'Local Authority Code'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Mapping the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019_merged, census_age)
names(Census_age_fp)
ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))

>>>>

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
head(census_age)
names(census_age)
```

```{r Plotting the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_fp)

# select the variables we want for clarity
df <- dplyr::select(Census_age_fp, LSOA11CD, "LA Name", "Proportion of households fuel poor (%)", "Proportion Over 65")

df$propFP <- as.numeric(substring(df$`Proportion Over 65`, 
                                  1, 
                                  nchar(df$`Proportion Over 65`)-1)
                        )

head(df)
# select the places we want

ggplot2::ggplot(df, aes(x=`Proportion of households fuel poor (%)`, 
               y=propFP)) +
  geom_point()
